\section{Experimental Set-up and Procedure}

\subsection{Part 1: Michelson interferometer}

As we have seen interference is crucial for this experiment (see \ref{Interference} ) and as we have further discussed coherence is an essential condition for that (see \ref{Coherence section}). So in the first part of the experiment we determine the Coherence Length of the light source to make sure that the path difference for object and reference beam won't be bigger than that in all following parts. Furthermore we will test how sensitive the set up is to disturbances.\\
As previously mentioned we will be using a Michelson interferometer for this part (see figure \ref{fig: Michelson} ). The light beam emitted from the Helium-Neon Laser encounters a beam splitter resulting in two beams propagating independently from one another. They are then reflected back on the beam splitter with a mirror, with both mirrors adjustable in distance (in a classical Michelson set up it is often just one mirror that is adjustable while the other is placed at a fixed distance from the beam splitter). After passing through the beam splitter they then hit a screen where an interference pattern is observed due to the path difference of both beams. However, the interference pattern will only be observed as long the beams are coherent which offers a straight forward way to measure the Coherence length: During the experiment we will change the path difference by moving the mirrors and thereby determine the Coherence length. Furthermore we will study the influence of disturbances such as noise, movement and a fire lighter.


%\graTwo[0.5]{coherence_length}{aufbau_michelson}{Set-up of Meassuring the Coherence Length with a Michelson interferometer \label{fig: Michelson} }


\subsection{Part 2: Double Exposure Hologram - Elastic Modulus of a Beam \label{DEH}}

The set-up used for this part of the experiment can be seen in figure \ref{DEH!}. The alignment of the spatial filters is the crucial part of the set-up and can take some time. A technique to get the spatial filters aligned is given in \cite{anleitung}.
The ratio of the intensities of reference and object bean could be adjusted by turning the beam splitter disk and should ideally be 10:1 at the position of recording the hologram. This can be verified with a photo diode. However, the photo diode turned out to be highly unreliable so that the ratio was estimated with the eye. A guideline can be that the reflection of the beam should just be bright enough to still be distinguishable from the reference beam on the photo plate which should be placed at Brewster angle with respect to the reference beam to minimize reflection. For glass this angle is $56 \degree$. Both beams should hit the centre of the photo plate.  

For the Double Exposure hologram three baths with developer, bleacher and water are prepared. Based on experience, we chose the following time intervals for the process of recording the hologram:

\begin{itemize}
	\item 
\end{itemize}


%\graTwo[0.5]{Versuchsaufbau_2}{aufbau-2}{top: Set-up for taking the holograms in part 2 and 3 of the experiment bottom: Set-up for taking the double-exposure hologram \label{DEH!}}

\subsection{Part 3: Real-time Holography - Oscillations of an Aluminium Plate \label{RTH}}

%\graX[0.7]{aufbau3}{Experimental Set-up part 3}{Set-up for taking the real-time hologram }{}
%
%\graX[0.4]{aufbauschaltung}{ Wiring for the resonance frequencies}{ Wiring for the resonance frequencies}
\subsection{Part 4: Fourier Interferometry \label{FI}}

%\graTwo[0.6]{Versuchsaufbau_4}{aufbau4}{Experimental set-up for the cross-correlation measurement}